SAYCAM preprocessing analyses from bounding box outputs

### 2022-01-06 preprocessing/step5_preprocess_fullset_from_bb_outputs.Rmd
full roi sweep
add code to get all dets for gold sample frames

@@

# cropping paramts
limit_lower =.2
limit_upper =.8
# vid params
y_max = 480
x_max = 640

@@

@@

   gold_sample_op<- gold_sample_op %>%
      right_join(gold_sample_op_center)[1:]

@@

all_thresholds = seq(0,.9,.1)

>>>>

```{r}
# cropping paramts
limit_lower =.2
limit_upper =.8
# vid params
y_max = 480
x_max = 640
```

@@

@@

   gold_sample_raw_dets <- this_vid_data %>%
     filter(frame %in% frames_to_get$frame) %>%
     mutate(vid_name = str_split(vid_name,"[.]")[[1]][1]) %>%
     group_by(frame, vid_name, child_id)

@@

   gold_sample_op<- gold_sample_op %>%
      right_join(gold_sample_op_center)

   # compile vid-level summaries 
   if (vid_index == 1){
     all_gold_sample_frames_op <- gold_sample_op
     gold_sample_all_dets <- gold_sample_raw_dets 
   }
   else if (vid_index > 1) {
   all_gold_sample_frames_op <- all_gold_sample_frames_op %>%
     full_join(gold_sample_op)

   gold_sample_all_dets <- gold_sample_all_dets %>%
     full_join(gold_sample_raw_dets)

   }
}
}
}
}
```

# Save it out
```{r}
# gold sample individual detections for each frame with position data
save(gold_sample_all_dets, file = here::here('data/preprocessed_data_2021/',paste0('gold_sample_all_indiivdual_dets.RData')))

```{r}

@@

all_thresholds = seq(0,.99,.01)
